### 2017-07-06 lafaySimulatedScenePerception.tex
translation of figure

\begin{figure}[t]
        \myfloatalign
        \includegraphics[width=.8\linewidth]{gfx/ch_4/3}
       \caption{Hierachical organisation of the isolated sounds used ofr the simulation.}\label{fig:orgDb}
\end{figure}

@@

\begin{figure}[t]
        \myfloatalign
        \includegraphics[width=\linewidth]{gfx/ch_5/5}
        \caption{Experimental protocol of the simulation experiment (1.a) and the pleasantness evaluation experiment (1.b)}\label{fig:xp1_2}
\end{figure}

@@

\begin{figure}[t]
        \myfloatalign
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_1}\label{fig:soundlevela}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_3}\label{fig:soundlevelb}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_5}\label{fig:soundlevelc}}\par
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_2}\label{fig:soundleveld}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_4}\label{fig:soundlevele}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_6}\label{fig:soundlevelf}}
       \caption{Distributions of the structural features $L$ (a, d), $L(E)$ (b, e) et $L(T)$ (c, f), with respect to scene type (a, b, c) and perceived pleasantness $\mathcal{A}_{scene}$ of experiments 1.b (d, e, f).}
\end{figure}

@@

\begin{figure}[t]
        \myfloatalign
        \subfloat[]
        {\includegraphics[width=1\linewidth]{gfx/ch_5/xp1_class_1_cam}\label{fig:soundsourcea}} \par
        \subfloat[]
        {\includegraphics[width=.4\linewidth]{gfx/ch_5/xp1_class_2_cam}\label{fig:soundsourceb}}
        \subfloat[]
        {\includegraphics[width=.4\linewidth]{gfx/ch_5/xp1_class_3_cam}\label{fig:soundsourcec}}
       \caption{Proportion of synthesized scenes (i or ni) involving a specific class of sounds: (a) event classes at an abstraction level $0+$, (b) texture classes at an abstraction level $0$, (c) event sub-classes at an abstraction level $1$ belonging to \emph{traffic} and \emph{public transportation} classes of the abstraction level $0$.}\label{fig:soundsource}
\end{figure}

@@

\begin{table}[t]
 \setlength{\tabcolsep}{0.2pt}
 \centering
  {\renewcommand{\arraystretch}{0.9}
\begin{tabular}{c c c c}
Abstraction        & \multicolumn{2}{c}{Event sound markers} \\
level & i-scenes & ni-scenes \\
\hline
0  &                          & construction work (3.78)  \\
\hline
  & church bell  (4.5)             & car horn  (3.9) \\
1 & bicycle bell  (4.3)      & siren (3.9)\\
  & animal (4.2)              &       \\
   \hline
  & bird        (4.8)       & car horn  (4.0)\\
2 & church bell  (4.4)             & siren (4.0)\\
  & bicycle bell     (4.2)             &       \\
   \hline
  & bird song (4.8)        & klaxon  (4.1)\\
3 & church bell   (4.3)            & siren (4.0)\\
  & bicycle bell      (4.2)   &       \\
  & foot steps  (3.6)      &  \\
  &                           & \\
  & \multicolumn{2}{c}{Texture sound markers}      \\
  & i-scenes & ni-scenes \\
\hline
0 &     courtyard / park (4.1) &  construction (3.9)  \\
\hline
1 &     park (3.65)          &  crossroad (3.6)  \\
  &                          &  construction vehicule (3.3)  \\
\hline
2 &     park (3.64)          &  crossroad (3.56)  \\
\hline
\end{tabular}
}
\vspace{0.5mm}
\caption{Event and texture classes identified as sound markers. In each cell, markers are ranked in the decreasing order of $V$ value.}
\label{tab:markers}
\end{table}

@@

\begin{figure}[t]
        \myfloatalign
        \includegraphics[width=\linewidth]{gfx/ch_5/pa5_1}
       \caption{$P@5$ obtained by considering the dissimilarity matrix computed from the paired Hamming distances of the semantic features vectors. The vectors are built by using all the classes ($ET$), only the event classes ($E$), only the texture classes ($T$), only the event classes corresponding to sound markers ($E_m$), or only the event classes excluding sound markers $E_{w/o,m}$.}\label{fig:pa5}
\end{figure}

@@

\begin{figure}[t]
        \myfloatalign
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_7}\label{fig:soundlevelMarkera}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_9}\label{fig:soundlevelNoisea}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_19}\label{fig:soundlevelMarkerDiffa}}\par
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_8}\label{fig:soundlevelMarkerd}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_10}\label{fig:soundlevelNoised}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_20}\label{fig:soundlevelMarkerDiffd}}
        \caption{Distribution of the relative sound levels structural features related to the presence of markers $L_m$ (a, d), $L(E)_m$ (b, e) and $L(T)_m$ (c, f), versus scene type (a, b, c) and perceived pleasantness $\mathcal{A}_{scene}$ of experiment 1.b (d, e, f).}\label{fig:soundlevelMarker}
\end{figure}

@@

\begin{figure}[h]
        \myfloatalign
        \subfloat[]
        {\includegraphics[width=.5\columnwidth]{gfx/ch_5/event_1}\label{fig:taxonomieEventa}}
        \subfloat[]
        {\includegraphics[width=.5\columnwidth]{gfx/ch_5/event_2}\label{fig:taxonomieEventb}}\par
        \subfloat[]
        {\includegraphics[width=.5\columnwidth]{gfx/ch_5/texture_1}\label{fig:taxonomieTexturea}}
        \subfloat[]
        {\includegraphics[width=.5\columnwidth]{gfx/ch_5/texture_2}\label{fig:taxonomieTextureb}}
       \caption{Taxonomies des classes de sons utilisées pour la simulation des environnements sonores urbains : (a,b) événements sonores et (c,d) textures sonores.}
       \label{fig:taxonomie}
\end{figure}

@@

\begin{figure}[h]
        \myfloatalign
        \subfloat[sujet 1]
        {\includegraphics[width=.24\linewidth]{gfx/ch_5/xp4_note_1}\label{fig:xp4_note_1a}}
        \subfloat[sujet 2]
        {\includegraphics[width=.24\linewidth]{gfx/ch_5/xp4_note_2}\label{fig:xp4_note_1b}}
        \subfloat[sujet 3]
        {\includegraphics[width=.24\linewidth]{gfx/ch_5/xp4_note_3}\label{fig:xp4_note_1c}}
        \subfloat[sujet 4]
        {\includegraphics[width=.24\linewidth]{gfx/ch_5/xp4_note_4}\label{fig:xp4_note_1d}} \par
        \subfloat[sujet 5]
        {\includegraphics[width=.24\linewidth]{gfx/ch_5/xp4_note_5}\label{fig:xp4_note_1e}}
        \subfloat[sujet 6]
        {\includegraphics[width=.24\linewidth]{gfx/ch_5/xp4_note_6}\label{fig:xp4_note_1f}}
        \subfloat[sujet 7]
        {\includegraphics[width=.24\linewidth]{gfx/ch_5/xp4_note_7}\label{fig:xp4_note_1g}}
        \subfloat[sujet 8]
        {\includegraphics[width=.24\linewidth]{gfx/ch_5/xp4_note_8}\label{}} \par
        \subfloat[sujet 9]
        {\includegraphics[width=.24\linewidth]{gfx/ch_5/xp4_note_9}\label{fig:xp4_note_1i}}
        \subfloat[sujet 10]
        {\includegraphics[width=.24\linewidth]{gfx/ch_5/xp4_note_10}\label{fig:xp4_note_1j}}
        \subfloat[sujet 11]
        {\includegraphics[width=.24\linewidth]{gfx/ch_5/xp4_note_11}\label{fig:xp4_note_1z}}
        \subfloat[sujet 12]
        {\includegraphics[width=.24\linewidth]{gfx/ch_5/xp4_note_12}\label{fig:xp4_note_1l}}
        \caption{Dispersions des notes données par les sujets lors de l'expérience 2 aux i/am-scènes (vert) et ni/am-scènes (rouge).}\label{fig:xp4_note_1}
\end{figure}

>>>>

\begin{figure}[t]
        \myfloatalign
        \includegraphics[width=.8\linewidth]{gfx/ch_4/3.png}
       \caption{Hierachical organisation of the isolated sounds used ofr the simulation.}\label{fig:orgDb}
\end{figure}

@@

\begin{figure}[t]
        \myfloatalign
        \includegraphics[width=\linewidth]{gfx/ch_5/5.png}
        \caption{Experimental protocol of the simulation experiment (1.a) and the pleasantness evaluation experiment (1.b)}\label{fig:xp1_2}
\end{figure}

@@

\begin{figure*}[t]
        \myfloatalign
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_1}\label{fig:soundlevela}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_3}\label{fig:soundlevelb}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_5}\label{fig:soundlevelc}}\par
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_2}\label{fig:soundleveld}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_4}\label{fig:soundlevele}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_6}\label{fig:soundlevelf}}
       \caption{Distributions of the structural features $L$ (a, d), $L(E)$ (b, e) et $L(T)$ (c, f), with respect to scene type (a, b, c) and perceived pleasantness $\mathcal{A}_{scene}$ of experiments 1.b (d, e, f).}
\end{figure*}

@@

\begin{figure}[t]
        \myfloatalign
        \subfloat[]
        {\includegraphics[width=1\linewidth]{gfx/ch_5/xp1_class_1}\label{fig:soundsourcea}} \par
        \subfloat[]
        {\includegraphics[width=.4\linewidth]{gfx/ch_5/xp1_class_2}\label{fig:soundsourceb}}
        \subfloat[]
        {\includegraphics[width=.4\linewidth]{gfx/ch_5/xp1_class_3}\label{fig:soundsourcec}}
       \caption{Proportion of synthesized scenes (i or ni) involving a specific class of sounds: (a) event classes at an abstraction level $0+$, (b) texture classes at an abstraction level $0$, (c) event sub-classes at an abstraction level $1$ belonging to \emph{traffic} and \emph{public transportation} classes of the abstraction level $0$.}\label{fig:soundsource}
\end{figure}

@@

\begin{table*}[t]
 \setlength{\tabcolsep}{0.2pt}
 \centering
  {\renewcommand{\arraystretch}{0.9}
\begin{tabular}{c c c c}
Abstraction        & \multicolumn{2}{c}{Event sound markers} \\
level & i-scenes & ni-scenes \\
\hline
0  &                          & construction work (3.78)  \\
\hline
  & church bell  (4.5)             & car horn  (3.9) \\
1 & bicycle bell  (4.3)      & siren (3.9)\\
  & animal (4.2)              &       \\
   \hline
  & bird        (4.8)       & car horn  (4.0)\\
2 & church bell  (4.4)             & siren (4.0)\\
  & bicycle bell     (4.2)             &       \\
   \hline
  & bird song (4.8)        & klaxon  (4.1)\\
3 & church bell   (4.3)            & siren (4.0)\\
  & bicycle bell      (4.2)   &       \\
  & foot steps  (3.6)      &  \\
  &                           & \\
  & \multicolumn{2}{c}{Texture sound markers}      \\
  & i-scenes & ni-scenes \\
\hline
0 &     courtyard / park (4.1) &  construction (3.9)  \\
\hline
1 &     park (3.65)          &  crossroad (3.6)  \\
  &                          &  construction vehicule (3.3)  \\
\hline
2 &     park (3.64)          &  crossroad (3.56)  \\
\hline
\end{tabular}
}
\vspace{0.5mm}
\caption{Event and texture classes identified as sound markers. In each cell, markers are ranked in the decreasing order of $V$ value.}
\label{tab:markers}
\end{table*}

@@

\begin{figure}[t]
        \myfloatalign
        \includegraphics[width=\linewidth]{gfx/ch_5/pa5_1_en}
       \caption{$P@5$ obtained by considering the dissimilarity matrix computed from the paired Hamming distances of the semantic features vectors as a function of the abstraction level. The vectors are built by using all the classes ($ET$), only the event classes ($E$), only the texture classes ($T$), only the event classes corresponding to sound markers ($E_m$), or only the event classes excluding sound markers $E_{w/o,m}$.}\label{fig:pa5}
\end{figure}

@@

\begin{figure*}[t]
        \myfloatalign
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_7}\label{fig:soundlevelMarkera}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_9}\label{fig:soundlevelNoisea}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_19}\label{fig:soundlevelMarkerDiffa}}\par
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_8}\label{fig:soundlevelMarkerd}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_10}\label{fig:soundlevelNoised}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_20}\label{fig:soundlevelMarkerDiffd}}
        \caption{Distribution of the relative sound levels structural features related to the presence of markers $L_m$ (a, d), $L(E)_m$ (b, e) and $L(T)_m$ (c, f), versus scene type (a, b, c) and perceived pleasantness $\mathcal{A}_{scene}$ of experiment 1.b (d, e, f).}\label{fig:soundlevelMarker}
\end{figure*}

@@

\begin{figure}[h]
        \myfloatalign
        \subfloat[]
        {\includegraphics[width=.5\columnwidth]{gfx/ch_5/event_1}\label{fig:taxonomieEventa}}
        \subfloat[]
        {\includegraphics[width=.5\columnwidth]{gfx/ch_5/event_2}\label{fig:taxonomieEventb}}\par
        \subfloat[]
        {\includegraphics[width=.5\columnwidth]{gfx/ch_5/texture_1}\label{fig:taxonomieTexturea}}
        \subfloat[]
        {\includegraphics[width=.5\columnwidth]{gfx/ch_5/texture_2}\label{fig:taxonomieTextureb}}
       \caption{Taxonomy of sound classes used for the simulation urban soundscapes: events (a,b) and textures (c,d).}
       \label{fig:taxonomie}
\end{figure}

@@

\begin{figure}[h]
        \myfloatalign
        \subfloat[subject 1]
        {\includegraphics[width=.24\linewidth]{gfx/ch_5/xp4_note_1}\label{fig:xp4_note_1a}}
        \subfloat[subject 2]
        {\includegraphics[width=.24\linewidth]{gfx/ch_5/xp4_note_2}\label{fig:xp4_note_1b}}
        \subfloat[subject 3]
        {\includegraphics[width=.24\linewidth]{gfx/ch_5/xp4_note_3}\label{fig:xp4_note_1c}}
        \subfloat[subject 4]
        {\includegraphics[width=.24\linewidth]{gfx/ch_5/xp4_note_4}\label{fig:xp4_note_1d}} \par
        \subfloat[subject 5]
        {\includegraphics[width=.24\linewidth]{gfx/ch_5/xp4_note_5}\label{fig:xp4_note_1e}}
        \subfloat[subject 6]
        {\includegraphics[width=.24\linewidth]{gfx/ch_5/xp4_note_6}\label{fig:xp4_note_1f}}
        \subfloat[subject 7]
        {\includegraphics[width=.24\linewidth]{gfx/ch_5/xp4_note_7}\label{fig:xp4_note_1g}}
        \subfloat[subject 8]
        {\includegraphics[width=.24\linewidth]{gfx/ch_5/xp4_note_8}\label{}} \par
        \subfloat[subject 9]
        {\includegraphics[width=.24\linewidth]{gfx/ch_5/xp4_note_9}\label{fig:xp4_note_1i}}
        \subfloat[subject 10]
        {\includegraphics[width=.24\linewidth]{gfx/ch_5/xp4_note_10}\label{fig:xp4_note_1j}}
        \subfloat[subject 11]
        {\includegraphics[width=.24\linewidth]{gfx/ch_5/xp4_note_11}\label{fig:xp4_note_1z}}
        \subfloat[subject 12]
        {\includegraphics[width=.24\linewidth]{gfx/ch_5/xp4_note_12}\label{fig:xp4_note_1l}}
        \caption{Distribution of scores given par the subjects during experiment 2 for i/am-scenes (green) et ni/am-scenes (red).}\label{fig:xp4_note_1}
\end{figure}
